Dear Hiring Manager at Citi,

I am writing to express my strong interest in the Learning Experience Designer position (Job Req ID 26933375) in Mississauga. Throughout my career spanning organizational transformation and team development, I have consistently championed adult learning and behavioral science principles to design scalable learning solutions that drive sustainable organizational change. Your mandate to build innovative, engaging leadership development experiences aligned with strategic priorities resonates deeply with my professional philosophy and proven track record.

In my current role as Senior Quality Director at Banque Nationale du Canada, I design and facilitate strategic change management programs that apply behavioral science principles to accelerate organizational adoption and culture transformation. I mentor and develop 5+ direct reports through structured coaching aligned with adult learning theory, ensuring each individual progresses meaningfully. Recognizing the complexity of matrixed global environments—managing stakeholder relationships across geographically distributed teams spanning Canada and Asia—I have consistently translated strategic organizational priorities into scalable, accessible learning initiatives. My focus on understanding stakeholder needs and influencing creative solution design has resulted in sustained adoption rates and measurable improvements in team capability and engagement metrics.

Earlier in my career, I served as a Consultant where I conducted needs analysis and change impact assessments, advising internal stakeholders on organizational adoption strategies and solution design. This consulting foundation strengthened my ability to partner effectively with diverse stakeholders, understand complex organizational trends, and design performance support tools that address genuine learning needs. I earned my Certified Scrum Master credential in 2024, equipping me to apply agile principles and design sprints—disciplines central to your iterative approach to developing formal programs and performance support tools.

What excites me most about joining Citi's Leadership Development team is the opportunity to leverage emerging technologies, particularly generative AI tools, to enhance learning design and development efficiency without compromising the human-centered focus essential to meaningful learning experiences. I am equally committed to establishing data-driven measurement systems—drawing from my hands-on experience building performance dashboards and analytics frameworks—to evaluate learning impact and inform stakeholders on program efficacy. Your emphasis on accessibility, cognitive load management, and inclusive design aligns with my conviction that learning solutions must balance engagement with practicality.

I am energized by the prospect of contributing my expertise in stakeholder management, change management, and adult learning principles to Citi's mission of building a continuous learning culture. I am available for discussion at your earliest convenience and would welcome the opportunity to explore how my background in organizational transformation can advance your strategic priorities. Thank you for considering my application.

Best regards,
Eric Mayeux
438-884-7645
mayeux.e@gmail.com
